---
title: "AdvanceML_Discussion_3"
author: "Ali Alghaithi"
date: "11/30/2020"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(fig.align='center', dpi=100, message=FALSE, warning=FALSE, cache=T,echo=T)
output <- opts_knit$get("rmarkdown.pandoc.to")
if(!is.null(output)) {
  if (output=="html") opts_chunk$set(out.width = '400px') else
    opts_chunk$set(out.width='.6\\linewidth')
}
set.seed(38380987)
```



# Reading the data
```{r}
library(readr)
library(dplyr)
creditcard <- read_csv("/Users/alialghaithi/Box/Advance NL Class/Discussion3/creditcard.csv")
head(creditcard)
```



```{r}
table(creditcard$Class)
```


```{r}
reduce_major <- creditcard %>% filter(creditcard$Class==0)
minority <- creditcard %>% filter(creditcard$Class==1)

for30 <- reduce_major[sample(nrow(reduce_major), ((nrow(minority)*100)/30)-nrow(minority)), ]
Data30 <- rbind(for30,minority)
Data30$Class <- as.factor(Data30$Class)
prop.table(table(Data30$Class))


for10 <- reduce_major[sample(nrow(reduce_major), ((nrow(minority)*100)/10)-nrow(minority)), ]
Data10 <- rbind(for10,minority)
Data10$Class <- as.factor(Data10$Class)
prop.table(table(Data10$Class))


for1 <- reduce_major[sample(nrow(reduce_major), ((nrow(minority)*100)/1)-nrow(minority)), ]
Data1 <- rbind(for1,minority)
Data1$Class <- as.factor(Data1$Class)
prop.table(table(Data1$Class))


# write.csv(Data1,"Data1.csv", row.names = FALSE)
# write.csv(Data10,"Data10.csv", row.names = FALSE)
# write.csv(Data30,"Data30.csv", row.names = FALSE)

```

# function for measurements 
```{r}
measurements <- function(real,pred,Name) {
Confusion_Matrix<- table(real,pred,dnn = c("Real", "y_pred"))
TN = Confusion_Matrix[1,1]
FN= Confusion_Matrix[2,1]
FP= Confusion_Matrix[1,2]
TP= Confusion_Matrix[2,2]

# True Negative Rate 
Acc_Negative = TN/(TN+FP)

# True Positive Rate
Acc_Positive = TP/(TP+FN)
Recall = Acc_Positive

# G-mean 
G_mean = (Acc_Negative * Acc_Positive)^(1/2)

# Precision
Precision = TP/(TP+FP)

# Weighted Accuracy
Beta= 0.5 # Here we use equal weights for both true positive rate and true negative rate; i.e., β equals 0.5
Weighted_Accuracy=  (Beta * Acc_Positive) + ((1-Beta)*Acc_Negative)

# F-measure
F_measure = (2 * Precision * Recall) /(Precision + Recall)

performance_measures <- data.frame("Method"= Name,"Acc_Positive(Recall)" =Acc_Positive, "Acc_Negative" = Acc_Negative, "Precision" = Precision,"F_measure" = F_measure,"G_mean" = G_mean,"Weighted_Accuracy" = Weighted_Accuracy)

return(performance_measures)

}

```


# =======================================================================================
# 30% Data
## Regular random forest
```{r}
set.seed(2020)
library(randomForest)
RegularRF30 <- randomForest(Class~., data=Data30)
table(Data30$Class,RegularRF30$predicted,dnn = c("Real", "y_pred"))
measurements(Data30$Class ,RegularRF30$predicted,"RegularRF30")

```

## Balanced random forest
```{r}
set.seed(2020)
# BRF cutoff=.2
sampsize = Data30  %>%filter(Class=="1") %>% nrow()
library(randomForest)
BRF30 <- randomForest(Class~., data=Data30, importance=TRUE,sampsize=sampsize,cutoff = c(0.3, 0.7),
                           replace = T)
table(Data30$Class , BRF30$predicted,dnn = c("Real", "y_pred"))

measurements(Data30$Class ,BRF30$predicted,"BRF30")
```



# =======================================================================================
# 10% Data
## Regular random forest
```{r}
set.seed(2020)
library(randomForest)
RegularRF10 <- randomForest(Class~., data=Data10)
table(Data10$Class,RegularRF10$predicted,dnn = c("Real", "y_pred"))
measurements(Data10$Class ,RegularRF10$predicted,"RegularRF10")

```

## Balanced random forest
```{r}
set.seed(2020)
# BRF cutoff=.2
sampsize = Data10  %>%filter(Class=="1") %>% nrow()
library(randomForest)
BRF10 <- randomForest(Class~., data=Data10, importance=TRUE,sampsize=sampsize,cutoff = c(0.3, 0.7),
                           replace = T)
table(Data10$Class , BRF10$predicted,dnn = c("Real", "y_pred"))

measurements(Data10$Class ,BRF10$predicted,"BRF10")
```
## Weighted random forest

# =======================================================================================
# 1% Data
## Regular random forest
```{r}
set.seed(2020)
library(randomForest)
RegularRF1 <- randomForest(Class~., data=Data1)
table(Data1$Class,RegularRF1$predicted,dnn = c("Real", "y_pred"))
measurements(Data1$Class ,RegularRF1$predicted,"RegularRF1")

```

## Balanced random forest
```{r}
set.seed(2020)
# BRF cutoff=.2
sampsize = Data1  %>%filter(Class=="1") %>% nrow()
library(randomForest)
BRF1 <- randomForest(Class~., data=Data1, importance=TRUE,sampsize=sampsize,cutoff = c(0.3, 0.7),
                           replace = T)
table(Data1$Class , BRF1$predicted,dnn = c("Real", "y_pred"))
measurements(Data1$Class ,BRF1$predicted,"BRF1")
```



# Comments

- After comparing the three methods, it shows that wghited Randomforest perforemd better than the other methods. And the balanced randomforest prfrme also better than th basic Randomforest. 

this approach of tuning randomforest to help it perfor better when we have unbalance data sets can be only useful when cosdiering yousing the randomforest alograthem. however, this opns a great way of learnign how to learn to have an alograthem that performs bad wiht unblanced data sets and make it work better. 


In adiiton, the more the positve class gets smaller, the more difiecult to fins the right values for tuning the cutoff and wighted class parameters. 
